### 2014-02-21 thesis/src/chapters/chapter-implementation.tex
Thesis: control loop sequence diagram

\newpage
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{System's deployment diagram}
  \label{fig:hlo-deployment}
\end{figure}

\section{Cloud brokerage subsystem}

\section{Auto-scaling subsystem}

@@

\subsection{Container manager}

@@

 \item execution - Manager adjusts container settings using an OpenVZ agent, located on computing node where container is deployed. As for OpenVZ hypervisor, container's properties are in fact User Bean Counter (UBC), exposed through a REST interface.
\end{itemize}

@@

CPU exceeds upper usage limit & \texttt{GREATER\_CPU} & Increase CPU \\ \hline
CPU is in legal range & \texttt{LESSER\_CPU} & Decrease CPU \\ \hline
CPU is lesser than allowed limit & \texttt{FITS\_CPU} & None \\ \hline

@@

\subsubsection{Control loop iteration}

\subsection{Stack manager}

@@

\subsection{Cloud instance manager}

\subsection{Cloud provider client}

\section{Cloud provider}

\section{Exemplary scenarios}

>>>>

\newpage
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-implementation/hlo-deployment}
  \end{center}
  \caption{System's deployment diagram}
  \label{fig:hlo-deployment}
\end{figure}
\newpage

% radek
\section{Cloud brokerage subsystem}

% darek
\section{Auto-scaling subsystem}

@@

% darek
\subsection{Container manager}

@@

 \item execution - Manager adjusts container settings using an OpenVZ agent, located on computing node where container is deployed. As for OpenVZ hypervisor, container's properties are User Bean Counter (UBC), exposed through a REST interface.
\end{itemize}

@@

CPU exceeds upper usage limit & \texttt{GREATER\_CPU} & Increase CPU \\ \hline
CPU is in legal range & \texttt{FITS\_CPU} & None \\ \hline
CPU is lesser than allowed & \texttt{LESSER\_CPU} & Decrease CPU \\ \hline

@@

Manager constantly loops through all aforementioned phases as depicted in figure \ref{fig:contanier-lifecycle-seq}.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-implementation/contanier-lifecycle-seq}
  \end{center}
  \caption{Sequence diagram illustrating container manager control loop}
  \label{fig:contanier-lifecycle-seq}
\end{figure}

% darek
\subsection{Stack manager}

\subsubsection{Objectives}
What lies in duties of a stack manager is:
\begin{itemize}
 \item supervising and scaling out stack
 \item delegating problem to a cloud instance manager, when not capable of resolving it
\end{itemize}

\subsubsection{Implementation details}

% radek
\subsection{Cloud instance manager}

@@

% darek
\subsection{Cloud provider client}

% darek
\section{Cloud provider}

% ?
\section{Exemplary scenarios}
